Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-08-15 doc/RMD/mlg-mcg.Rmd
Add rectangle to mcg plot delimiting 8 MCGs

```{r barplots, fig.width = 10, fig.height = 5}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), desc(count)) %>%
  rename(Type = type) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLGs", 0.5, 0.85)), color = "black", position = "identity") +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  # scale_alpha(breaks = c(0.5, 0.75, 1)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  # coord_flip() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.major.y = element_line(color = "grey50")) +
  theme(panel.grid.minor.y = element_line(color = "grey70")) +
  theme(legend.box.just = "top") +
  theme(legend.box.margin = unit(c(0, 6.55, 0, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = "white", color = "black")) +
  theme(legend.box = "horizontal") +
  theme(aspect.ratio = 1/2) +
  labs(list(
    alpha = "MLG\nEvenness"
  ))

@@

mcg_graph_inset <- cowplot::ggdraw() + 
  cowplot::draw_plot(mcg_graph, 0, 0, 1, 1) + 
  cowplot::draw_plot(even, 0.75, 0.5675, 0.25, 0.4)
mcg_graph_inset
if (!interactive()){
  cowplot::ggsave(mcg_graph_inset, 
                  filename = file.path(PROJHOME, "results/figures/publication/mcg-barplot.pdf"),
                  width = 10,
                  height = 5)
  # pdf(file.path(PROJHOME, "results/figures/publication/Figure1Z.pdf"), width = 10, height = 5)
  # print(mcg_graph)
  # print(even, vp = vp1)
  # dev.off()
}
```

@@

```{r subgraphs, fig.height = 10, fig.width = 8}
mcg_theme <- theme(legend.text = element_text(size = 10)) +
  theme(legend.title = element_text(size = 10)) +
  theme(axis.text.x = element_blank()) +
  # theme(legend.background = element_blank()) +
  # theme(legend.box.background = element_blank()) +
  theme(legend.key.size = unit(0.5, "line")) +
  theme(legend.position = c(0.9, 0.5)) +
  theme(legend.box = "vertical") +
  theme(legend.box.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(legend.spacing = unit(0, "lines")) + 
  theme(aspect.ratio = 0.45) +
  theme(plot.background = element_rect(color = "black", fill = "grey98"))
mcg_subgraph_with_context <- cowplot::ggdraw(xlim = c(0, 2), ylim = c(0, 2.25)) +
  cowplot::draw_plot(t5g, 0, -0.125, 2, 2) +
  cowplot::draw_plot(mcg_graph + scale_alpha(breaks = c(0.5, 0.75, 1)) + mcg_theme, 0, 1.45, 1.35, 1) +
  cowplot::draw_plot(mcg_mlg_graph2, x = 1.355, y = 1.633, width = 0.6345, height = 0.6345) +
  cowplot::draw_plot_label(c("A", "B", "C"), x = c(0, 1.35, 0), y = c(2.25, 2.25, 1.65), size = 25)
mcg_subgraph_with_context
if (!interactive()){
  cowplot::ggsave(plot = mcg_subgraph_with_context,
                  filename = file.path(PROJHOME, "results", "figures", "publication", "mcg-subgraph-with-context.pdf"),
                  width = 8, 
                  height = 10)
}
```

>>>>

```{r barplots, fig.width = 10, fig.height = 5}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), desc(count)) %>%
  rename(Type = type) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLGs", 0.5, 0.85)), color = "black", position = "identity") +
  annotate(geom = "rect", xmin = 0.5, xmax = 8.5, ymin = 0, ymax = 75, color = "black", size = 1.5, alpha = 0, lty = 2) +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  # scale_alpha(breaks = c(0.5, 0.75, 1)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  # coord_flip() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.major.y = element_line(color = "grey50")) +
  theme(panel.grid.minor.y = element_line(color = "grey70")) +
  theme(legend.box.just = "top") +
  theme(legend.box.margin = unit(c(0, 6.55, 0, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = "white", color = "black")) +
  theme(legend.box = "horizontal") +
  theme(legend.position = c(0.77, 0.75)) +
  theme(aspect.ratio = 1/2) +
  labs(list(
    alpha = "MLG\nEvenness"
  ))

@@

mcg_graph_inset <- cowplot::ggdraw() + 
  cowplot::draw_plot(mcg_graph, 0, 0, 1, 1) + 
  cowplot::draw_plot(even, 0.75, 0.5675, 0.25, 0.4)
mcg_graph_inset
if (!interactive()){
  cowplot::ggsave(mcg_graph_inset, 
                  filename = file.path(PROJHOME, "results/figures/publication/mcg-barplot.pdf"),
                  width = 10,
                  height = 5,
                  units = "in")
  # pdf(file.path(PROJHOME, "results/figures/publication/Figure1Z.pdf"), width = 10, height = 5)
  # print(mcg_graph)
  # print(even, vp = vp1)
  # dev.off()
}
```

@@

```{r subgraphs, fig.height = 10, fig.width = 8}
greyground <- theme(plot.background = element_rect(color = "black", fill = "grey98"))
mcg_theme <- theme(legend.text = element_text(size = 10)) +
  theme(legend.title = element_text(size = 10)) +
  theme(axis.text.x = element_blank()) +
  # theme(legend.background = element_blank()) +
  theme(legend.box.background = element_rect(fill = "grey98")) +
  theme(legend.key.size = unit(0.75, "line")) +
  theme(legend.box.just = "left") +
  theme(legend.position = c(0.9, 0.5)) +
  theme(legend.box = "vertical") +
  theme(legend.box.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(legend.spacing = unit(0, "lines")) +
  theme(aspect.ratio = 0.45) +
  greyground
mcg_subgraph_with_context <- cowplot::ggdraw(xlim = c(0, 2), ylim = c(0, 2.25)) +
  cowplot::draw_plot(t5g, 0, -0.125, 2, 2) +
  cowplot::draw_plot(mcg_graph + scale_alpha(breaks = c(0.5, 0.75, 1)) + mcg_theme, 0, 1.45, 1.35, 1) +
  cowplot::draw_plot(mcg_mlg_graph2 + greyground, x = 1.355, y = 1.633, width = 0.6345, height = 0.6345) +
  cowplot::draw_plot_label(c("A", "B", "C"), x = c(0, 1.35, 0), y = c(2.25, 2.25, 1.65), size = 25)
mcg_subgraph_with_context
if (!interactive()){
  cowplot::ggsave(plot = mcg_subgraph_with_context,
                  filename = file.path(PROJHOME, "results", "figures", "publication", "mcg-subgraph-with-context.pdf"),
                  width = 8, 
                  height = 10)
}
```
